Beyond clines: lineages and haplotype blocks in hybrid zones

### 2016-04-24 drafts/hybrid_zone.tex
some changes

\begin{figure}
\includegraphics{figs/alleleFrequencies_sim.pdf}
\caption{
    Frequency of ancestry $B$,
    across geography at different physical positions on the genome, simulated for a hybrid zone
     $T=100$ generations after secondary contact, with $s=0.1$,
     using 50 demes, each with 500 diploid individuals and $\sigma=1$.
    Each line represents a locus some distance $r$ away from the true target of selection.
    Grey lines represent the same positions from a simulation with
    identical parameters except that $s=0$.
    Corresponding theoretical quantities are shown juxtaposed in Figure \ref{sfig:alleleFreq_tau100_comparison};
    the same plot is shown with weaker selection in Figure \ref{alleleFreq_tau100_weaker_s} and at a longer time in Figure \ref{alleleFreq_tau1000}.
}\label{alleleFreq_tau100}
\end{figure}

@@

\begin{figure}
\includegraphics{figs/number_of_ancestors_tau1000.pdf}
\caption{\textbf{Mean family size of haplotypes.} The number of individuals of ancestry $B$ per number of ancestors ($F_B(m,x)$) from secondary contact occurring $T=1000$ generations ago, represented across geographic space. The hybrid zone is 50 demes, each containing 500 diploid individuals.
 Each red or orange line represents a site some distance away (ranging from 0 - 0.01) from the selected site (here $s=0.01$ and $\sigma=1$). Yellow lines are corresponding positions on an unlinked chromosome with no selected loci, and grey lines are corresponding positions in a simulation with no selection.  Bold lines depict the target of selection when present, and corresponding position on chromosomes not harboring any selected sites.}\label{Fig:family_size}
\end{figure}

>>>>

\begin{figure}
\includegraphics{figs/alleleFrequencies_sim_comparison_revision_original.pdf}
    \caption{
        \textbf{Comparison of simulated to theoretical clines:}
        As in Figure \ref{alleleFreq_tau100},
        frequency of ancestry $B$,
        across geography and at several physical positions on the genome,
        at $T=100$ generations after secondary contact,
        and at $s=0.1$.
        Dotted lines are expected frequencies of $B$ ancestry $1-q(x,t,r)$
        (unconditional on the ancestry of the linked allele), computed numerically.
        Each line represents a locus some distance $r$ away from the true target of selection, 
        and $r=0$ represents the locus that is under selection.    
    }\label{sfig:alleleFreq_tau100_comparison}
\end{figure}

@@

\begin{figure}
\includegraphics{figs/number_of_ancestors_tau1000.pdf}
\caption{\textbf{Mean family size of haplotypes.} The number of individuals of ancestry $B$ per number of ancestors ($F_B(m,x)$) from secondary contact occurring $T=1000$ generations ago, represented across geographic space. The hybrid zone is 50 demes, each containing 500 diploid individuals.
 Each red or orange line represents a site some distance away (ranging from 0 - 0.5cM) from the selected site (here $s=0.01$ and $\sigma=1$). Yellow lines are corresponding positions on an unlinked chromosome with no selected loci, and grey lines are corresponding positions in a simulation with no selection.  Bold lines depict the target of selection when present, and corresponding position on chromosomes not harboring any selected sites.}\label{Fig:family_size}
\end{figure}

### 2016-04-24 drafts/supplement.tex
made some revisions
some changes

\begin{figure}
    \includegraphics{figs/alleleFrequencies_sim_comparison.pdf}
    \caption{
        \textbf{Comparison of simulated to theoretical clines:}
        As in Figure \ref{alleleFreq_tau100},
        frequency of ancestry $B$,
        across geography and at several physical positions on the genome,
        at $T=100$ generations after secondary contact,
        and at $s=0.1$.
        Dotted lines are expected frequencies of $B$ ancestry $1-q(x,t,r)$
        (unconditional on the ancestry of the linked allele), computed numerically.
        Each line represents a locus some distance $r$ away from the true target of selection, 
        and $r=0$ represents the locus that is under selection.    
    }\label{sfig:alleleFreq_tau100_comparison}
\end{figure}

@@

>>>>

\begin{figure}
    \includegraphics{figs/alleleFrequencies_sim.pdf}
    \caption{
    Frequency of ancestry $B$,
    across geography at different physical positions on the genome, simulated for a hybrid zone
     $T=100$ generations after secondary contact, with $s=0.1$,
     using 50 demes, each with 500 diploid individuals and $\sigma=1$.
    Each line represents a locus some distance $r$ away from the true target of selection.
    Grey lines represent the same positions from a simulation with
    identical parameters except that $s=0$.
    Corresponding theoretical quantities are shown juxtaposed in Figure \ref{sfig:alleleFreq_tau100_comparison};
    the same plot is shown with weaker selection in Figure \ref{alleleFreq_tau100_weaker_s} and at a longer time in Figure \ref{alleleFreq_tau1000}.
}\label{alleleFreq_tau100}
\end{figure}

@@

\begin{figure}
    \includegraphics{figs/s001_adjacentBlocksAlongChromAncBConditioning}
    \includegraphics{figs/s001_adjacentBlocksAlongChromNoConditioningHighRes}
        \caption{
     Block lengths along chromosome under $s=0.001$, conditioning on ancestry B (upper) and without conditioning (lower) alisa{is this perhaps an instance where we would need to have more demes to see a signal?
    }
    } \label{sfig:blockLengthPlot_t1000_s0.001}
\end{figure}
